\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-10 k-planar.tex
Small fries

\referee{1}{3. Theorem 10: Unfortunately I have to suggest removing it. I don’t see the motivation for making $H$ planar or for improving the constants. Are the improved constants at all close to tight? Is there another reason for including it?}

\note{DW}{We can motivate \cref{1-planar} since the graph drawing community particularly cares about 1-planar graphs, since treewidth 3 is best possible, and since the planarity of $H$ is essential in the proof of \cref{1PlanarQueue}. Futher motivation comes from the open problem at the end of the paper. We need to argue this in the response and in the paper. The alternative is to remove \cref{sec-1-planar}? We could keep the statement of \cref{1-planar} in the paper and refer to the arXiv paper for the proof. What do you think? All this depends on whether we can fix the errors below. I vote to fix the errors, add more motivation for \cref{1-planar}, keep the theorem and the proof. }

@@

\note{PM}{I agree that we should fix it and keep it.  Another reason: For vertex ranking, the bound is $O(\log n/\log^{(t)} n)$ where $t:=\tw(H)$, so this is an example where $\tw(H)$ affects more than just the constant.}

>>>>

% \referee{1}{3. Theorem 10: Unfortunately I have to suggest removing it. I don’t see the motivation for making $H$ planar or for improving the constants. Are the improved constants at all close to tight? Is there another reason for including it?}
% 
% \note{DW}{We can motivate \cref{1-planar} since the graph drawing community particularly cares about 1-planar graphs, since treewidth 3 is best possible, and since the planarity of $H$ is essential in the proof of \cref{1PlanarQueue}. Futher motivation comes from the open problem at the end of the paper. We need to argue this in the response and in the paper. The alternative is to remove \cref{sec-1-planar}? We could keep the statement of \cref{1-planar} in the paper and refer to the arXiv paper for the proof. What do you think? All this depends on whether we can fix the errors below. I vote to fix the errors, add more motivation for \cref{1-planar}, keep the theorem and the proof. }

@@

% \note{PM}{I agree that we should fix it and keep it.  Another reason: For vertex ranking, the bound is $O(\log n/\log^{(t)} n)$ where $t:=\tw(H)$, so this is an example where $\tw(H)$ affects more than just the constant.}
